### 2017-10-06 Project1/LaTeX/report.tex
Added report

\documentclass[times]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{float}
\usepackage{placeins}
\usepackage[none]{hyphenat}
\usepackage{amsmath}
\usepackage[us]{datetime}
\usepackage[explicit]{titlesec}
%\titleformat{\section}{\normalfont}{}{0em}{\textbf{\large Problem  \thesection}\  \normalsize #1}
\begin{document}
	\title{CS 6601 Secure Data Analysis - Fall 2017 \\ Project 1 \\ Millionaire Problem using Garbled Circuits}
	\author{Adam Bowers \\ Sammie Bush \\ Dalton Cole}
	\date{\formatdate{6}{10}{2017}}
	\maketitle

	\section{Implementation}
	Our main worker for this project is the \textit{h1Circuit.py} script. What this script does is create the input files for GCParser. The needed input files are: \textit{millionaireCircuit.cir}, \textit{partyOneInputFile}, and \textit{partyTwoInputFile}. The purpose of these files are: the main input file, the client's input, and the server's input, respectively.

	All results of the experiment can be seen in the result's directory. The \textit{siclientout} and \textit{siserverout} correspond party 1 and party 2, respectively.

\end{document}

### 2017-10-06 Project1/GCParser/src/GCParser/generated_files/CircuitParser.java

@@ -10,6 +10,9 @@
 
     private Variable_Context context;
 
+    private int major_version;
+    private int minor_version;
+
     private int lineNumber;
     private boolean errors;
     private int partyComp = Input_Variable.ALL;
@@ -126,36 +129,37 @@
 
   final public void GarbledCircuit() throws ParseException, CircuitDescriptionException, FileNotFoundException, IOException {
   OperationNameResolver.initOperations();
+    Version_Line();
     label_1:
     while (true) {
-      switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
-      case COMMENT:
-      case INPUT_MARK:
-      case LINE_ENDING:
-        ;
-        break;
-      default:
-        jj_la1[0] = jj_gen;
-        break label_1;
-      }
       switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
       case INPUT_MARK:
         InputLine();
         break;
       default:
-        jj_la1[1] = jj_gen;
+        jj_la1[0] = jj_gen;
         ;
       }
       LineEnding();
+      switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
+      case LINE_ENDING:
+      case INPUT_MARK:
+      case COMMENT:
+        ;
+        break;
+      default:
+        jj_la1[1] = jj_gen;
+        break label_1;
+      }
     }
     OutputLine();
     LineEnding();
     label_2:
     while (true) {
       switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
-      case COMMENT:
-      case OUTPUT_MARK:
       case LINE_ENDING:
+      case OUTPUT_MARK:
+      case COMMENT:
         ;
         break;
       default:
@@ -176,8 +180,8 @@
     label_3:
     while (true) {
       switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
-      case COMMENT:
       case LINE_ENDING:
+      case COMMENT:
         ;
         break;
       default:
@@ -186,9 +190,9 @@
       }
       LineEnding();
       switch ((jj_ntk==-1)?jj_ntk():jj_ntk) {
+      case INCLUDE:
       case START_PARTY:
       case END_PARTY:
-      case INCLUDE:
       case IDENTIFIER:
         Calculation();
         break;
@@ -205,13 +209,31 @@
     }
   }
 
[…]

### 2017-10-06 Project1/GCParser/src/GCParser/generated_files/CircuitParserConstants.java

@@ -11,41 +11,41 @@ public interface CircuitParserConstants {
   /** End of File. */
   int EOF = 0;
   /** RegularExpression Id. */
-  int COMMENT = 4;
+  int COLON = 4;
   /** RegularExpression Id. */
-  int INPUT_MARK = 5;
+  int PERIOD = 5;
   /** RegularExpression Id. */
-  int OUTPUT_MARK = 6;
+  int COMMA = 6;
   /** RegularExpression Id. */
-  int START_PARTY = 7;
+  int LINE_ENDING = 7;
   /** RegularExpression Id. */
-  int END_PARTY = 8;
+  int OPEN_PAREN = 8;
   /** RegularExpression Id. */
-  int SIGNED_MARK = 9;
+  int CLOSE_PAREN = 9;
   /** RegularExpression Id. */
-  int UNSIGNED_MARK = 10;
+  int INPUT_MARK = 10;
   /** RegularExpression Id. */
-  int LINE_ENDING = 11;
+  int OUTPUT_MARK = 11;
   /** RegularExpression Id. */
-  int INCLUDE = 12;
+  int SIGNED_MARK = 12;
   /** RegularExpression Id. */
-  int PATH = 13;
+  int INCLUDE = 13;
   /** RegularExpression Id. */
-  int OPEN_PAREN = 14;
+  int VERSION = 14;
   /** RegularExpression Id. */
-  int CLOSE_PAREN = 15;
+  int UNSIGNED_MARK = 15;
   /** RegularExpression Id. */
-  int COLON = 16;
+  int START_PARTY = 16;
   /** RegularExpression Id. */
-  int COMMA = 17;
+  int END_PARTY = 17;
   /** RegularExpression Id. */
-  int IDENTIFIER = 18;
+  int PATH = 18;
   /** RegularExpression Id. */
-  int INTEGER = 19;
+  int IDENTIFIER = 19;
   /** RegularExpression Id. */
-  int DIGITS = 20;
+  int INTEGER = 20;
   /** RegularExpression Id. */
-  int LETTER = 21;
+  int COMMENT = 21;
 
   /** Lexical state. */
   int DEFAULT = 0;
@@ -56,24 +56,24 @@ public interface CircuitParserConstants {
     "\" \"",
     "\"\\t\"",
     "\"\\r\"",
-    "<COMMENT>",
-    "\".input\"",
-    "\".output\"",
[…]

### 2017-10-06 Project1/GCParser/src/GCParser/generated_files/CircuitParserTokenManager.java

@@ -19,65 +19,65 @@ private final int jjStopStringLiteralDfa_0(int pos, long active0)
    switch (pos)
    {
       case 0:
-         if ((active0 & 0x600L) != 0L)
+         if ((active0 & 0x9000L) != 0L)
          {
-            jjmatchedKind = 18;
-            return 11;
+            jjmatchedKind = 19;
+            return 4;
          }
          return -1;
       case 1:
-         if ((active0 & 0x600L) != 0L)
+         if ((active0 & 0x9000L) != 0L)
          {
-            jjmatchedKind = 18;
+            jjmatchedKind = 19;
             jjmatchedPos = 1;
-            return 11;
+            return 4;
          }
          return -1;
       case 2:
-         if ((active0 & 0x600L) != 0L)
+         if ((active0 & 0x9000L) != 0L)
          {
-            jjmatchedKind = 18;
+            jjmatchedKind = 19;
             jjmatchedPos = 2;
-            return 11;
+            return 4;
          }
          return -1;
       case 3:
-         if ((active0 & 0x600L) != 0L)
+         if ((active0 & 0x9000L) != 0L)
          {
-            jjmatchedKind = 18;
+            jjmatchedKind = 19;
             jjmatchedPos = 3;
-            return 11;
+            return 4;
          }
          return -1;
       case 4:
-         if ((active0 & 0x600L) != 0L)
+         if ((active0 & 0x9000L) != 0L)
          {
-            jjmatchedKind = 18;
+            jjmatchedKind = 19;
             jjmatchedPos = 4;
-            return 11;
+            return 4;
          }
          return -1;
       case 5:
-         if ((active0 & 0x400L) != 0L)
+         if ((active0 & 0x1000L) != 0L)
+            return 4;
+         if ((active0 & 0x8000L) != 0L)
          {
-            jjmatchedKind = 18;
+            jjmatchedKind = 19;
             jjmatchedPos = 5;
-            return 11;
+            return 4;
          }
-         if ((active0 & 0x200L) != 0L)
-            return 11;
          return -1;
       case 6:
-         if ((active0 & 0x400L) != 0L)
+         if ((active0 & 0x8000L) != 0L)
          {
-            jjmatchedKind = 18;
[…]

### 2017-10-06 Project1/h1CiruitGenerator.py

@@ -1,6 +1,5 @@
-#Python file to generate circuit file
-#to compute secure dot product given number of terms
-#and number of bits of each term
+# Python file to generate circuit file to compute secure dot product
+# given number of terms and number of bits of each term.
 
 import sys
 import os

### 2017-10-18 Project2/h2CircuitGenerator.py
Fixed bit size probelm

@@ -39,6 +39,8 @@ def main():
 			max_input = max(max_input, i)
 	while(pow(2, numBitsForInput) - 1 < max_input):
 		numBitsForInput += 1
+	numBitsForInput *= 2
+	numBitsForInput += len(data['party1']) - 1
 
 	# File names
 	outFileName = "secureDotProduct.cir"

### 2017-10-19 Project1/h1CiruitGenerator.py
took a stab at multiplication

@@ -1,0 +1,50 @@
+# Python file to generate circuit file to compute secure dot product
+# given number of terms and number of bits of each term.
+
+import sys
+import os
+import subprocess
+
+def main():
+    if(len(sys.argv)!= 5):
+        print('Error except 4 arguments full path to script running circuit, the number of bits for inputs, party1 input and party2 input')
+        return
+    numBitsForInput = int(sys.argv[2])
+    outFileName = "millionaireCircuit.cir"
+    outInputFileName = "partyOneInputFile"
+    outInput2FileName = "partyTwoInputFile"
+
+    outText = ""
+    #generate input block
+    outText = outText + ".input a 1 "+str(numBitsForInput)+"\n"
+    outText = outText + ".input b 2 "+str(numBitsForInput)+"\n"
+    #then output block
+    outText = outText + "\n"
+    outText = outText + ".output firstPartyGreater"+"\n"
+
+    #then computation block
+    outText = outText + "\n"
+    outText = outText + "firstPartyGreater gts a b"+"\n"
+
+    #now write to a file, program will crash if it doesn't open for some reasons
+    with open(outFileName,'w') as f:
+        f.write(outText)
+
+    outText = ""
+    outText += "b "+sys.argv[4] + "\n"
+
+    # now write to a file, program will crash if it doesn't open for some reasons
+    with open(outInputFileName, 'w') as f:
+        f.write(outText)
+
+    # now write to a file, program will crash if it doesn't open for some reasons
+    outText = ""
+    outText += "a "+sys.argv[3] + "\n"
+    with open(outInput2FileName, 'w') as f:
+        f.write(outText)
+    #now execute the code
+    os.system("./runCircuit "+sys.argv[1]+" ./"+outFileName +" ./"+ outInputFileName +" ./"+ outInput2FileName)
+    #subprocess.call(["./runCircuit",sys.argv[1]+" ./"+outFileName +" ./"+ outInputFileName +" ./"+ outInput2FileName])
+
+if __name__ == "__main__":
+    main()

### 2017-10-19 Project2/h2CircuitGenerator.py

@@ -20,7 +20,7 @@ def main():
 	if(len(sys.argv)!= 3):
 		print('Usage: python3 h2CircuitGenerator.py config.json <GCParser location>')
 		return
-
+	print("starting")
 	# Json dictionary of {party1: [ints], party2: [ints]}
 	data = {}
 	with open(sys.argv[1], 'r') as data_file:    
@@ -94,11 +94,11 @@ def main():
 		f.write(outText)
 
 	with open(outInput1FileName, 'w') as f:
-		f.write(party1outText)
-
-	with open(outInput2FileName, 'w') as f:
 		f.write(party2outText)
 
+	with open(outInput2FileName, 'w') as f:
+		f.write(party1outText)
+	print(" running " +"./runCircuit " + sys.argv[2] + " ./" + outFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
 	os.system("./runCircuit " + sys.argv[2] + " ./" + outFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
 
 

### 2017-10-19 Project2/test.py

@@ -1,0 +1,73 @@
+#Python file to generate circuit file
+#to compute secure dot product given number of terms
+#and number of bits of each term
+
+import math
+
+def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
+    text = ""
+    #first have to extend to proper number of bits
+    #text+= "sextend "+term1+" "+str(maxNeededBits)+"\n"
+    #text+= "sextend "+term2+" "+str(maxNeededBits)+"\n"
+    text+= run+"formatted"+term2+" sextend "+term2+" "+str(maxNeededBits)+"\n"
+    #now go bit by bit to get total
+    for i in range(0,numBits):
+        curLoop =str(i)
+        text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
+        #now extend for 8 additions
+        text+= run+"curBitExt"+curLoop+" sextend "+run+"curBit"+curLoop+" "+str(maxNeededBits)+"\n"
+        #now have to add curBit to itself numbits time
+        for k in range(0,numBits):
+            if (k == 0):
+                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(maxNeededBits) + "\n"
+            else:
+                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" add " +run+"additionResult"+curLoop+chr(ord('a') +(k-1))\
+                        + " "+run+"curBitExt"+curLoop+"\n"
+        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and "+run+"additionResult"+curLoop+chr(ord('a') +(numBits-1))\
+                +" "+run+"formatted"+term2+"\n"
+        if(i==0):
+            text+= run+"multiplicationResult"+curLoop+" sextend "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
+                   +" "+str(maxNeededBits)+"\n"
+        else:
+            #shift left by i and
+            #we add i zeroes then make sure same length for addition
+            text+= run+"multiplicationResult"+curLoop+" add "+run+"multiplicationResult"+str(i-1)+\
+                   " "+run + "additionResult" + curLoop + chr(ord('a') + numBits)+"\n"
+
+    return text
+
+
+def main():
+    numBitsForInput = 3
+    numTerms = 3
+    outText = ""
[…]

### 2017-10-19 Project2/test.py
got it running result still wrong

@@ -15,31 +15,35 @@ def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
         curLoop =str(i)
         text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
         #now extend for 8 additions
-        text+= run+"curBitExt"+curLoop+" sextend "+run+"curBit"+curLoop+" "+str(maxNeededBits)+"\n"
+        text+= run+"curBitExt"+curLoop+" sextend "+run+"curBit"+curLoop+" "+str(numBits)+"\n"
         #now have to add curBit to itself numbits time
         for k in range(0,numBits):
             if (k == 0):
-                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(maxNeededBits) + "\n"
+                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(numBits) + "\n"
             else:
                 text += run+"additionResult"+curLoop+chr(ord('a') +k)+" add " +run+"additionResult"+curLoop+chr(ord('a') +(k-1))\
                         + " "+run+"curBitExt"+curLoop+"\n"
-        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and "+run+"additionResult"+curLoop+chr(ord('a') +(numBits-1))\
-                +" "+run+"formatted"+term2+"\n"
+        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"additionResult"+curLoop+chr(ord('a') +(numBits-1)) \
+                + " " +term2 + "\n"
         if(i==0):
             text+= run+"multiplicationResult"+curLoop+" sextend "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
                    +" "+str(maxNeededBits)+"\n"
         else:
             #shift left by i and
+            text+= run + "additionResultShifted" + curLoop+chr(ord('a')+numBits) +" zextend "+" "+run + "additionResult"+ \
+                   curLoop + chr(ord('a') + numBits)+ " "+str(numBits+i) +"\n"
+            text+= run + "additionResultFinal" + curLoop+chr(ord('a')+numBits) + " sextend "+ \
[…]

### 2017-10-19 Project2/test.py
added multiplication

@@ -9,31 +9,34 @@ def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
     #first have to extend to proper number of bits
     #text+= "sextend "+term1+" "+str(maxNeededBits)+"\n"
     #text+= "sextend "+term2+" "+str(maxNeededBits)+"\n"
-    text+= run+"formatted"+term2+" sextend "+term2+" "+str(maxNeededBits)+"\n"
     #now go bit by bit to get total
     for i in range(0,numBits):
         curLoop =str(i)
         text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
         #now extend for 8 additions
-        text+= run+"curBitExt"+curLoop+" sextend "+run+"curBit"+curLoop+" "+str(numBits)+"\n"
+        #text+= run+"curBitExt"+curLoop+" concat " 0:"+str(numBits-1)+" "+run+"curBit"+curLoop+"\n"
+        text+= run+"curBitExt"+curLoop+" concat "
+        for k in range(0,numBits):
+            text+= run+ "curBit"+curLoop+ " "
+        text+="\n"
         #now have to add curBit to itself numbits time
+        '''
         for k in range(0,numBits):
             if (k == 0):
                 text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(numBits) + "\n"
             else:
                 text += run+"additionResult"+curLoop+chr(ord('a') +k)+" add " +run+"additionResult"+curLoop+chr(ord('a') +(k-1))\
                         + " "+run+"curBitExt"+curLoop+"\n"
-        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"additionResult"+curLoop+chr(ord('a') +(numBits-1)) \
+        '''
+        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"curBitExt"+curLoop \
                 + " " +term2 + "\n"
         if(i==0):
-            text+= run+"multiplicationResult"+curLoop+" sextend "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
-                   +" "+str(maxNeededBits)+"\n"
+            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
[…]

### 2017-10-20 Project2/multiplicationCircuitGenerator.py
changed circuit generator to be included in Dalton's wrapper

@@ -1,0 +1,82 @@
+#Python file to generate circuit file
+#to compute secure dot product given number of terms
+#and number of bits of each term
+
+import math
+
+#generates line of circuit files for multiplication between term1 and term2
+#numbits is number of bits for term1 and term2
+# maxneededBits is highest number of bits needed for multiplication between the two
+# and run is a unique string identifier for this multiplication to generate unique
+#variable names required by gcparser
+def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
+    text = ""
+    #before bit by bit multiplication according to
+    #https://en.wikipedia.org/wiki/Binary_multiplier
+    for i in range(0,numBits):
+        curLoop =str(i)
+        #first we get the current bit
+        text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
+        #and extend it to our bit length
+        text+= run+"curBitExt"+curLoop+" concat "
+        for k in range(0,numBits):
+            text+= run+ "curBit"+curLoop+ " "
+        text+="\n"
+        #then and with other term to get multiplication result for this bit
+        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"curBitExt"+curLoop \
+                + " " +term2 + "\n"
+        #and finally add it to our running total
+        if(i==0):
+            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
+                   +"\n"
+        else:
+            #shift left by i and
+            text+= run + "additionResultFinal" + curLoop+chr(ord('a')+numBits) + " concat 0:"+str(maxNeededBits-numBits-i)+" "+ \
+                   run + "additionResult" + curLoop + chr(ord('a') + numBits) + " 0:"+str(i) + "\n"
+            #we add i zeroes then make sure same length for addition
+            text+= run+"multiplicationResult"+curLoop+" add "+run+"multiplicationResult"+str(i-1)+\
+                   " "+run + "additionResultFinal" + curLoop+ chr(ord('a') + numBits)+"\n"
+
+    return text
+
+#function that writes out to outputFile the circuit for secure dot product
+#with two vectors each with unsigned int input of numBitsForInput and
+#having numTerms terms
[…]

### 2017-10-20 Project2/test.py

@@ -1,80 +1,0 @@
-#Python file to generate circuit file
-#to compute secure dot product given number of terms
-#and number of bits of each term
-
-import math
-
-def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
-    text = ""
-    #first have to extend to proper number of bits
-    #text+= "sextend "+term1+" "+str(maxNeededBits)+"\n"
-    #text+= "sextend "+term2+" "+str(maxNeededBits)+"\n"
-    #now go bit by bit to get total
-    for i in range(0,numBits):
-        curLoop =str(i)
-        text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
-        #now extend for 8 additions
-        #text+= run+"curBitExt"+curLoop+" concat " 0:"+str(numBits-1)+" "+run+"curBit"+curLoop+"\n"
-        text+= run+"curBitExt"+curLoop+" concat "
-        for k in range(0,numBits):
-            text+= run+ "curBit"+curLoop+ " "
-        text+="\n"
-        #now have to add curBit to itself numbits time
-        '''
-        for k in range(0,numBits):
-            if (k == 0):
-                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(numBits) + "\n"
-            else:
-                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" add " +run+"additionResult"+curLoop+chr(ord('a') +(k-1))\
-                        + " "+run+"curBitExt"+curLoop+"\n"
-        '''
-        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"curBitExt"+curLoop \
-                + " " +term2 + "\n"
-        if(i==0):
-            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
-                   +"\n"
-        else:
-            #shift left by i and
-            text+= run + "additionResultFinal" + curLoop+chr(ord('a')+numBits) + " concat 0:"+str(maxNeededBits-numBits-i)+" "+ \
-                   run + "additionResult" + curLoop + chr(ord('a') + numBits) + " 0:"+str(i) + "\n"
-            #we add i zeroes then make sure same length for addition
[…]

### 2017-10-20 Project2/h2CircuitGenerator.py
Dalton thing

@@ -42,6 +42,9 @@ def main():
 	numBitsForInput *= 2
 	numBitsForInput += len(data['party1']) - 1
 
+	generateCircuitForFile(data['threshold'], "secureDotProduct.cir", numBitsForInput, len(data['party1']))
+
+	"""
 	# File names
 	outFileName = "secureDotProduct.cir"
 	outInput1FileName = "partyOneInputFile"
@@ -100,7 +103,7 @@ def main():
 		f.write(party1outText)
 	print(" running " +"./runCircuit " + sys.argv[2] + " ./" + outFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
 	os.system("./runCircuit " + sys.argv[2] + " ./" + outFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
-
+	"""
 
 if __name__ == "__main__":
 	main()

### 2017-10-20 Project2/h2CircuitGenerator.py
both integrated now need to create submission and documentation

@@ -7,103 +7,100 @@ import os
 import subprocess
 import json
 from collections import deque
-
-def generateMultiplicationforNBitNumbers(numBits,var1,var2):
-	text = ""
-	#not sure how to do this yet but final result should be in variable called
-	#multiplicationResult
-	for i in range(0,numBits):
-		text = text + " result"
+from multiplicationCircuitGenerator import generateCircuitForFile
 
 def main():
-	# Need config.json as a parameter
-	if(len(sys.argv)!= 3):
-		print('Usage: python3 h2CircuitGenerator.py config.json <GCParser location>')
-		return
-	print("starting")
-	# Json dictionary of {party1: [ints], party2: [ints]}
-	data = {}
-	with open(sys.argv[1], 'r') as data_file:    
-		data = json.load(data_file)
+    # Need config.json as a parameter
+    if(len(sys.argv)!= 3):
+        print('Usage: python3 h2CircuitGenerator.py config.json <GCParser location>')
+        return
+    print("starting")
+    # Json dictionary of {t:int numBitsForInput: int party1: [ints], party2: [ints]}
+    data = {}
+    with open(sys.argv[1], 'r') as data_file:
+        data = json.load(data_file)
 
-	for key, value in data.items():
-		# Convert party1 and party 2 to a list of ints
-		data[key] = list(map(int, data[key].split(',')))
+    for key, value in data.items():
+        # Convert party1 and party 2 to a list of ints
+        data[key] = list(map(int, data[key].split(',')))
 
-	# Find max number of bits
-	numBitsForInput = 2
-	max_input = 0
+    # Find max number of bits
+    '''
+    numBitsForInput = 2
+    max_input = 0
 
-	for key, value in data.items():
-		for i in value:
-			max_input = max(max_input, i)
-	while(pow(2, numBitsForInput) - 1 < max_input):
-		numBitsForInput += 1
-	numBitsForInput *= 2
-	numBitsForInput += len(data['party1']) - 1
+    for key, value in data.items():
+        for i in value:
+            max_input = max(max_input, i)
+    while(pow(2, numBitsForInput) - 1 < max_input):
+        numBitsForInput += 1
+    numBitsForInput *= 2
+    numBitsForInput += len(data['party1']) - 1
+    '''
+    circuitFileName = "secureDotProduct.cir"
[…]

### 2017-10-20 Project2/multiplicationCircuitGenerator.py

@@ -46,12 +46,13 @@ def generateCircuitForFile(outputFile,numBitsForInput,numTerms):
     outText = ""
     #calculate max possible bits needed for operations
     maxNeededMultiplicationBits = 2*numBitsForInput
+    print(maxNeededMultiplicationBits)
     maxNeededSumBits = maxNeededMultiplicationBits+int(math.ceil(math.log(maxNeededMultiplicationBits,2)))
     #now make the circuit file
     with open(outputFile,'w') as f:
 
         # generate input block
-        outText += ".input t 2 "+str(maxNeededSumBits)
+        outText += ".input t 2 "+str(maxNeededSumBits)+"\n"
         for i in range(0,numTerms):
             outText = outText + ".input party1Term"+str(i)+" 2 "+str(numBitsForInput)+"\n"
             outText = outText + ".input party2Term"+str(i)+" 1 "+str(numBitsForInput)+"\n"
@@ -79,4 +80,6 @@ def generateCircuitForFile(outputFile,numBitsForInput,numTerms):
                 outText += "finalResult"+str(i)+" add finalResult"+str(i-1)+" finalResultInterExt"+str(i)+"\n"
             f.write(outText)
             outText = ""
-        outText+= "greaterOrEqualTo gteu finalResult"+str(numTerms-1)+" t"
+        outText+= "greaterOrEqualToT gteu finalResult"+str(numTerms-1)+" t"+"\n"
+        f.write(outText)
+        outText = ""

### 2017-10-20 Project2/LaTeX/report.tex
Latex

\documentclass[times]{article}

\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{float}
\usepackage{placeins}
\usepackage[none]{hyphenat}
\usepackage{amsmath}
\usepackage[us]{datetime}
\usepackage[explicit]{titlesec}
\usepackage{url}
\begin{document}
	\title{CS6601  - Fall 2017 \\ Project 2}
	\author{Adam Bowers \\ Sammie Bush \\ Dalton Cole}
	\date{\formatdate{20}{10}{2017}}
	\maketitle

	For this project, the goal is to see if a dot product between two vectors is greater than or equal to some threshold. The vectors and thresholds are specified in \textit{config.json}. To accomplish bit multiplication, we implemented \cite{ref:mult}. The basic principle is thus: for each bit in A (the first number), multiply that bit by B (the second number) and store it in $C_i$ where i starts at 0. Bit shift each $C_i$ left by i. Finally, add each number together using bit addition. This will generate the final product. To do a dot product, add up each multiplication result. This will yield $D$, the dot product. To finish the circuit, we compare $D$ to the threshold value specified in the configuration file. If $D$ is greater than the set threshold, then a value of 1 will be outputted, 0 otherwise.

	For the threshold value, it is assumed that the number of bits will be no greater than the max number of bits that the dot product can take. The formula used to calculate the max number of bits for the dot product is shown in Equation \ref{equ:bits}.

	\begin{equation}
		\label{equ:bits}
		2 * \textnormal{bits of largest number} + ciel(lg(\textnormal{Vector Size - 1}))
	\end{equation}

	\medskip
	\bibliographystyle{plain}
	\bibliography{bib}

\end{document}

### 2017-10-20 GCParser/test.py

@@ -1,0 +1,80 @@
+#Python file to generate circuit file
+#to compute secure dot product given number of terms
+#and number of bits of each term
+
+import math
+
+def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
+    text = ""
+    #first have to extend to proper number of bits
+    #text+= "sextend "+term1+" "+str(maxNeededBits)+"\n"
+    #text+= "sextend "+term2+" "+str(maxNeededBits)+"\n"
+    #now go bit by bit to get total
+    for i in range(0,numBits):
+        curLoop =str(i)
+        text = text + run+ "curBit"+curLoop+" select "+ term1+" "+ str(i)+" "+str(i+1)+"\n"
+        #now extend for 8 additions
+        #text+= run+"curBitExt"+curLoop+" concat " 0:"+str(numBits-1)+" "+run+"curBit"+curLoop+"\n"
+        text+= run+"curBitExt"+curLoop+" concat "
+        for k in range(0,numBits):
+            text+= run+ "curBit"+curLoop+ " "
+        text+="\n"
+        #now have to add curBit to itself numbits time
+        '''
+        for k in range(0,numBits):
+            if (k == 0):
+                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" select "+run+"curBitExt"+curLoop+" 0" + " " + str(numBits) + "\n"
+            else:
+                text += run+"additionResult"+curLoop+chr(ord('a') +k)+" add " +run+"additionResult"+curLoop+chr(ord('a') +(k-1))\
+                        + " "+run+"curBitExt"+curLoop+"\n"
+        '''
+        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"curBitExt"+curLoop \
+                + " " +term2 + "\n"
+        if(i==0):
+            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
+                   +"\n"
+        else:
+            #shift left by i and
+            text+= run + "additionResultFinal" + curLoop+chr(ord('a')+numBits) + " concat 0:"+str(maxNeededBits-numBits-i)+" "+ \
+                   run + "additionResult" + curLoop + chr(ord('a') + numBits) + " 0:"+str(i) + "\n"
+            #we add i zeroes then make sure same length for addition
[…]

### 2017-10-20 Project2/h2CircuitGenerator.py
nice clean code with stuff working

@@ -1,6 +1,7 @@
-# Python file to generate circuit file
-# to compute secure dot product given number of terms
-# and number of bits of each term
+# Python file to generate circuit file and input files
+#then execute them given a jsonfile(format specified belo
+#and the path to Gcparser on the system
+
 
 import sys
 import os
@@ -25,18 +26,23 @@ def main():
         data[key] = list(map(int, data[key].split(',')))
 
     # Find max number of bits
-    '''
+
     numBitsForInput = 2
     max_input = 0
-
-    for key, value in data.items():
-        for i in value:
-            max_input = max(max_input, i)
-    while(pow(2, numBitsForInput) - 1 < max_input):
+    if(len(data['party1'])!=len(data['party2'])):
+        print("both parties must have same number of items")
+        quit()
+    #now make sure properly allocated bits
+    for value in data['party1']:
+        max_input = max(max_input, value)
+    for value in data['party2']:
+        max_input = max(max_input, value)
+    while(pow(2, numBitsForInput)-1 < max_input):
         numBitsForInput += 1
-    numBitsForInput *= 2
-    numBitsForInput += len(data['party1']) - 1
-    '''
+    if(numBitsForInput>data['numBitsForInput'][0]):
+        print("Invalid number of bits allocated for inputs ")
+        quit()
+
     circuitFileName = "secureDotProduct.cir"
     generateCircuitForFile( circuitFileName, data['numBitsForInput'][0], len(data['party1']))
 
@@ -50,57 +56,24 @@ def main():
     party1outText = "t "+str(data['t'][0])+"\n"
     party2outText = ""
 
-    # Generate input block
+    # Generate input files for server and client
     input_index = 0
     for value in data['party1']:
         #outText += ".input party1a" + str(input_index) + " 1 " + str(numBitsForInput) + '\n'
         party1outText += "party1Term" + str(input_index) + " " + str(value) + '\n'
         input_index += 1
-
-
     input_index = 0
     for value in data['party2']:
-        # outText += ".input party2b" + str(input_index) + " 2 " + str(numBitsForInput) + '\n'
         party2outText += "party2Term" + str(input_index) + " " + str(value) + '\n'
         input_index += 1
     with open(outInput1FileName, 'w') as f:
         f.write(party1outText)
-
     with open(outInput2FileName, 'w') as f:
         f.write(party2outText)
[…]

### 2017-10-20 Project2/multiplicationCircuitGenerator.py

@@ -23,19 +23,19 @@ def generateMultiplicationforNBitNumbers(term1,term2,numBits,maxNeededBits,run):
             text+= run+ "curBit"+curLoop+ " "
         text+="\n"
         #then and with other term to get multiplication result for this bit
-        text+=  run+"additionResult"+curLoop+chr(ord('a') +numBits)+" and " +run+"curBitExt"+curLoop \
+        text+=  run+"additionResult"+curLoop+" and " +run+"curBitExt"+curLoop \
                 + " " +term2 + "\n"
         #and finally add it to our running total
         if(i==0):
-            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop+chr(ord('a') +numBits)\
+            text+= run+"multiplicationResult"+curLoop+" concat 0:"+str(maxNeededBits-numBits)+" "+run+"additionResult"+curLoop\
                    +"\n"
         else:
             #shift left by i and
-            text+= run + "additionResultFinal" + curLoop+chr(ord('a')+numBits) + " concat 0:"+str(maxNeededBits-numBits-i)+" "+ \
-                   run + "additionResult" + curLoop + chr(ord('a') + numBits) + " 0:"+str(i) + "\n"
+            text+= run + "additionResultFinal" + curLoop + " concat 0:"+str(maxNeededBits-numBits-i)+" "+ \
+                   run + "additionResult" + curLoop + " 0:"+str(i) + "\n"
             #we add i zeroes then make sure same length for addition
             text+= run+"multiplicationResult"+curLoop+" add "+run+"multiplicationResult"+str(i-1)+\
-                   " "+run + "additionResultFinal" + curLoop+ chr(ord('a') + numBits)+"\n"
+                   " "+run + "additionResultFinal" + curLoop +"\n"
 
     return text
 
@@ -46,11 +46,9 @@ def generateCircuitForFile(outputFile,numBitsForInput,numTerms):
     outText = ""
     #calculate max possible bits needed for operations
     maxNeededMultiplicationBits = 2*numBitsForInput
-    print(maxNeededMultiplicationBits)
-    maxNeededSumBits = maxNeededMultiplicationBits+int(math.ceil(math.log(maxNeededMultiplicationBits,2)))
+    maxNeededSumBits = maxNeededMultiplicationBits+int(math.ceil(math.log(maxNeededMultiplicationBits,2)))*2
[…]

### 2017-10-20 Project2/LaTeX/report.tex
Report?
Added plus 1 to report

@@
 
-	For the threshold value, it is assumed that the number of bits will be no greater than the max number of bits that the dot product can take.
+	For the threshold value, it is assumed that the number of bits will be no greater than the max number of bits plus 1 that the dot product can take.
 The formula used to calculate the max number of bits for the dot product is shown in Equation \ref{equ:bits}.
@@
 
+	All inputs are assumed to be unsigned integers as required by the project description.
+
 	\medskip

### 2017-10-20 Project2/multiplicationCircuitGenerator.py
added some final tweaks

@@ -46,7 +46,8 @@ def generateCircuitForFile(outputFile,numBitsForInput,numTerms):
     outText = ""
     #calculate max possible bits needed for operations
     maxNeededMultiplicationBits = 2*numBitsForInput
-    maxNeededSumBits = maxNeededMultiplicationBits+int(math.ceil(math.log(maxNeededMultiplicationBits,2)))*2
+    #adding one bit in case t is right at threshold
+    maxNeededSumBits = maxNeededMultiplicationBits+int(math.ceil(math.log(maxNeededMultiplicationBits,2)))*2 +1
     #now make the circuit file
     with open(outputFile,'w') as f:
         # generate input block
@@ -56,7 +57,8 @@ def generateCircuitForFile(outputFile,numBitsForInput,numTerms):
             outText = outText + ".input party2Term"+str(i)+" 1 "+str(numBitsForInput)+"\n"
         #then output block
         outText = outText + "\n"
-        outText = outText + ".output finalResult"+str(numTerms-1)+"\n"
+		#uncomment this line if you want to see the final product
+        #outText = outText + ".output finalResult"+str(numTerms-1)+"\n"
         outText = outText + ".output greaterOrEqualToT"+"\n"
         outText = outText + "\n"
         f.write(outText)

### 2017-10-20 Project2/h2CircuitGenerator.py
final version of files for submission

@@ -73,6 +73,8 @@ def main():
     #now run the generated gc circuit
     print(" running " + "./runCircuit " + sys.argv[
         2] + " " + circuitFileName + " " + outInput1FileName + " " + outInput2FileName)
+	#need to set circuit file to executable
+    os.chmod("runCircuit",0666)
     os.system("./runCircuit " + sys.argv[2] + " ./" + circuitFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
 
 if __name__ == "__main__":

### 2017-10-20 Project2/h2CircuitGenerator.py
change how permission set

@@ -74,7 +74,7 @@ def main():
     print(" running " + "./runCircuit " + sys.argv[
         2] + " " + circuitFileName + " " + outInput1FileName + " " + outInput2FileName)
 	#need to set circuit file to executable
-    os.chmod("runCircuit",0666)
+    os.system("chmod +x runCircuit")
     os.system("./runCircuit " + sys.argv[2] + " ./" + circuitFileName + " ./" + outInput1FileName + " ./" + outInput2FileName)
 
 if __name__ == "__main__":

### 2017-11-27 hw2/h2.tex
started h2

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[10pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{HW2}
\author{Adam Bowers, Dalton Cole, Sammie Bush}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\subsection*{\textbf{PseudoCode}}
Let l be the bit length of u\&v, and let 1 be most significant bit and l least significant bit.
Part 1\\
Party one randomly chooses functionality F=u>v or u<v
He first computes 
\begin{itemize}
	\item for i=1 to l 
		\begin{itemize}
			\item $E_{pk} (u_i * v_i ) \gets SM(E_{pk} (u_i) , E_{pk}(v_i))$
			\\ first party one computes the same product of current bit of v and u
			\item if selected F: was u$>$v
			 \subitem $W_i \gets E_{pk} (u_i) * E_{pk} (u_i * v_i)^{n-1}$
			 \\compute $u_i - u_i*v_i $
			 \subitem $\Gamma_i \gets E_{pk}(v_i - u_i) * E_{pk}(r_i)$ where $r_i \in Z_n$
			 \\compute $v_i - u_i +r_i$
			\item else
			\subitem $W_i \gets E_{pk} (v_i) * E_{pk} (u_i * v_i)^{N-1}$
			\\compute $v_i - u_i*v_i $
			\subitem $\Gamma_i \gets E_{pk}(u_i - v_i) * E_{pk}(r_i)$ where $r_i \in Z_n$
			\\compute $u_i - v_i +r_i$
			\item $G_i \gets E_{pk}(u_i \oplus v_i)$
			\\now compute xor of two bits if 0 they're the same so first 1 tells us first different bit
			\item $H_i \gets H_{i-1}^{s_i} * G_i ;$ where $s_i \in Z_n$ and $H_0 = E_{pk}(0)$
			\\now mask the xor based on previous bits and a random number
			\item $\Phi_i \gets E_{pk}(-1) * H_i$
			\\ \textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a dont care?}
			\item $L_i \gets W_i * \Phi_i^{t_i}$ where $t_i \in Z_n$
			\\ compute final product to share with party two if term one and term two don't match $\Phi$ will be zero so $L_i$ is 1 otherwise it will be a junk term
		\end{itemize}
	\item  $\Gamma' \gets \pi_1(\Gamma)$
	\item $L' \gets \pi_2(L)$
	\item send $\Gamma' \& L'$ to P2
\end{itemize}
Part 2\\
Party two computes
\begin{itemize}
	\item $M \gets D_{sk}(L_i')$
	\\decrypt our Ls
	\item if there exists an $M_i=1$
		\subitem $\alpha \gets 1$
	\item else
		\subitem $\alpha \gets 0$
	\\assign alpha based on L values
	\item $M_i' \gets \Gamma_i^{\alpha '} for 1\le i \le l$
	\\if we have a 1 in M then P1 gets $Gamma'$ back 
	\item send $M'$ and $E_{pk}(alpha)$ to P1
\end{itemize}
Part 3\\
\begin{itemize}
	\item $M \gets \pi^{-1}(M')$
	\\un permute M
	\item for i= 1 to l
		\subitem $\lambda_i \gets M_i * E_{pk}(\alpha)^{N-r_i}$
		\\if alpha = 1 we subtract the random value added to L in part one
		\subitem if F = $u>v$ 
			\subitem $E_{pk}(min(u,v)_i) \gets E_{pk}(u_i) * \lambda_i$
		\subitem else
			\subitem $E_{pk}(min(u,v)_i) \gets E_{pk}(v_i) * \lambda_i$
	\item concat $E_{pk}(min(u,v)_i)$ and Party one has $E_{pk}(min(u,v))$ as required

\end{itemize}
\subsection*{\textbf{Description}}

\subsection*{\textbf{Example}}

\end{document}

### 2017-11-28 hw2/h2.tex
expanded on descriptions

@@
 			\item $E_{pk} (u_i * v_i ) \gets SM(E_{pk} (u_i) , E_{pk}(v_i))$
-			\\ first party one computes the same product of current bit of v and u
+			\\ first party one computes the product of current bit of v and u
 			\item if selected F: was u$>$v
 			 \subitem $W_i \gets E_{pk} (u_i) * E_{pk} (u_i * v_i)^{n-1}$
-			 \\compute $u_i - u_i*v_i $
+			 \\compute $u_i - u_i*v_i $ if there is any $W_i=1$ we know for i $u_i=1$ \& $v_i=0$
 			 \subitem $\Gamma_i \gets E_{pk}(v_i - u_i) * E_{pk}(r_i)$ where $r_i \in Z_n$
@@
 			\subitem $W_i \gets E_{pk} (v_i) * E_{pk} (u_i * v_i)^{N-1}$
-			\\compute $v_i - u_i*v_i $
+			\\compute $v_i - u_i*v_i $  if there is any $W_i=1$ we know for i $v_i=1$ \& $u_i=0$
 			\subitem $\Gamma_i \gets E_{pk}(u_i - v_i) * E_{pk}(r_i)$ where $r_i \in Z_n$
@@
 			\item $H_i \gets H_{i-1}^{s_i} * G_i ;$ where $s_i \in Z_n$ and $H_0 = E_{pk}(0)$
-			\\now mask the xor based on previous bits and a random number
+			\\now mask the xor based on previous bits and a random number, Hs will be 0 till first 1 then every term past that will be a random value based on $s$ values.
 			\item $\Phi_i \gets E_{pk}(-1) * H_i$
-			\\ \textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a dont care?}
+			\\shift the domain of by n-1
+			 \textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a random value?}
 			\item $L_i \gets W_i * \Phi_i^{t_i}$ where $t_i \in Z_n$
-			\\ compute final product to share with party two if term one and term two don't match $\Phi$ will be zero so $L_i$ is 1 otherwise it will be a junk term
+			\\ if $W_i$ is 1 $\Phi_i^{t_i}$ will be 0 thus $L_i$ will be 1 otherwise it will be some random value 
 		\end{itemize}
@@
 	\item $L' \gets \pi_2(L)$
+	\\we permute the outputs so P2 can't tell anything from indices of bits
 	\item send $\Gamma' \& L'$ to P2
@@
 		\subitem $\alpha \gets 0$
-	\\assign alpha based on L values
+	\\assign alpha based on L values. If there is a 1 we know the selected F function of P1
+	\\is true but not what it is
 	\item $M_i' \gets \Gamma_i^{\alpha '} for 1\le i \le l$
-	\\if we have a 1 in M then P1 gets $Gamma'$ back 
+	\\if we have a 1 in M then P1 gets $Gamma$ back, otherwise they get random values
 	\item send $M'$ and $E_{pk}(alpha)$ to P1
@@
 		\\if alpha = 1 we subtract the random value added to L in part one
+		\\to get either $v-u$ or $u-v$ depending on f chosen
 		\subitem if F = $u>v$ 
 			\subitem $E_{pk}(min(u,v)_i) \gets E_{pk}(u_i) * \lambda_i$
+			\\if $u>v$ $\lambda$ = $v-u$ if $v>u$ otherwise 0
+			\\therefore $u_i +\lambda_i$ gives us bit of highest value
 		\subitem else
 			\subitem $E_{pk}(min(u,v)_i) \gets E_{pk}(v_i) * \lambda_i$
+			\\if $v>u$ $\lambda$ = $u-v$ if $u>v$ otherwise 0
+			\\therefore $v_i +\lambda_i$ gives us bit of highest value
 	\item concat $E_{pk}(min(u,v)_i)$ and Party one has $E_{pk}(min(u,v))$ as required

### 2017-12-01 hw2/normal_min.py
Working on secure min

@@ -1,0 +1,10 @@
+from random import sample, randrange
+
+### Person 1 ###
+possible_functionalities = ["u less v", "v less u"]
+
+# (a)
+functionality = sample(possible_functionalities)
+print("Functionality: {}".fomrat(functionality))
+
+# (b)

### 2017-12-01 hw2/secure_minimum.py

@@ -1,0 +1,134 @@
+from random import randrange, choice, shuffle
+from phe import paillier
+
+# Pretend everyting is encrypted because -.-
+
+# Z_n
+N = 13
+
+# Bit length
+l = 3
+
+# Generate pailliar keys
+public_key, private_key = paillier.generate_paillier_keypair()
+
+def secure_multiplication(a, b):
+	### Party 1 ###
+	ra = randrange(0, N)
+	rb = randrange(0, N)
+
+	a_prime = (a + public_key.encrypt(ra))
+	b_prime = (b + public_key.encrypt(rb))
+
+	### Party 2 ###
+	h_a = private_key.decrypt(a_prime)
+	h_b = private_key.decrypt(b_prime)
+
+	h = (h_a * h_b) % N
+	h_prime = public_key.encrypt(h)
+
+	### Party 1 ###
+	s = h_prime + (a * (N - rb))
+	s_prime = s + (b * (N - ra))
+	a_times_b = s_prime + (public_key.encrypt(ra * rb) * (N - 1))
+
+	return a_times_b
+
+def minimum(u, v):
+	### Party 1 ###
+	# Randomly choose functionality
+	f = choice(["u > v"])#, "u < v"])
+
+	# String formating for l bits 
+	bit_str = '{:0' + str(l) + 'b}'
+
+	# Initalize H_0
+	h_i = public_key.encrypt(0)
+
+	# Random s and t
+	s = []
+	t = []
+
+	# L list
+	L = []
+
+	for i in range(l):
+		# Assume we can get each bit out of encrypted text
+		u_i = public_key.encrypt(int(bit_str.format(x)[i]))
+		v_i = public_key.encrypt(int(bit_str.format(y)[i]))
+
+		# Secure minimum
+		e_ui_times_vi = secure_multiplication(u_i, v_i)
+		#print(private_key.decrypt(e_ui_times_vi) % N)
+
+		# Assign w_i based on f
+		w_i = 0
+		if f == 'u > v':
+			w_i = u_i + (e_ui_times_vi * (N - 1))
+		else:
+			w_i = v_i + (e_ui_times_vi * (N - 1))
+
+		# G_i
+		g_i = public_key.encrypt(int(bit_str.format(x)[i]) ^ int(bit_str.format(y)[i]))
+
+		# H_i
+		s.append(randrange(0, N))
+		h_i = (h_i * s[-1]) + g_i
+
+		# Phi
[…]

### 2017-12-01 hw2/h2.tex

@@
 	\\if we have a 1 in M then P1 gets $Gamma$ back, otherwise they get random values
-	\item send $M'$ and $E_{pk}(alpha)$ to P1
+	\item send $M'$ and $E_{pk}(\alpha)$ to P1
 \end{itemize}
@@
 \end{itemize}
+
+\subsection*{\textbf{Two Phase Version}}
+Let l be the bit length of u\&v, and let 1 be most significant bit and l least significant bit.
+Furthermore let BD be a secure Binary Decomposition function \& SM be a secure multiplication function
+
+Phase one of the protocol returns E(0) if u is the minimum and E(1) if v is the minimum or equal to u.
+
+\textbf{(Minimum(E(u),E(v))}
+\\where E(u) and E(v) are encrypted bitwise
+Part 1\\
+Party one randomly chooses functionality F=u>v or u<v
+He first computes 
+\begin{itemize}
+	\item for i=1 to l 
+	\begin{itemize}
+		\item $E_{pk} (u_i * v_i ) \gets SM(E_{pk} (u_i) , E_{pk}(v_i))$
+		\\ first party one computes the product of current bit of v and u
+		\item if selected F: was u$>$v
+		\subitem $W_i \gets E_{pk} (u_i) * E_{pk} (u_i * v_i)^{n-1}$
+		\\compute $u_i - u_i*v_i $ if there is any $W_i=1$ we know for i $u_i=1$ \& $v_i=0$
+		\item else
+		\subitem $W_i \gets E_{pk} (v_i) * E_{pk} (u_i * v_i)^{N-1}$
+		\\compute $v_i - u_i*v_i $  if there is any $W_i=1$ we know for i $v_i=1$ \& $u_i=0$
+		\item $G_i \gets E_{pk}(u_i \oplus v_i)$
+		\\now compute xor of two bits if 0 they're the same so first 1 tells us first different bit
+		\item $H_i \gets H_{i-1}^{s_i} * G_i ;$ where $s_i \in Z_n$ and $H_0 = E_{pk}(0)$
+		\\now mask the xor based on previous bits and a random number, Hs will be 0 till first 1 then every term past that will be a random value based on $s$ values.
+		\item $\Phi_i \gets E_{pk}(-1) * H_i$
+		\\shift the domain of by n-1
+		\textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a random value?}
+		\item $L_i \gets W_i * \Phi_i^{t_i}$ where $t_i \in Z_n$
+		\\ if $W_i$ is 1 $\Phi_i^{t_i}$ will be 0 thus $L_i$ will be 1 otherwise it will be some random value 
+	\end{itemize}
+	\item $L' \gets \pi_2(L)$
+	\\we permute the output so P2 can't tell anything from indices of bits
+	\item send $L'$ to P2
+\end{itemize}
+Part 2\\
+Party two computes
+\begin{itemize}
+	\item $M \gets D_{sk}(L_i')$
+	\\decrypt our Ls
+	\item if there exists an $M_i=1$
+	\subitem $\alpha \gets 1$
+	\item else
+	\subitem $\alpha \gets 0$
+	\\assign alpha based on L values. If there is a 1 we know the selected F function of P1
+	\\is true but not what it is
+	\item send $E_{pk}(\alpha)$ to P1
+\end{itemize}
+Part 3\\
+\\if alpha is one function is true 0 false, map that to
+\\0 if u is min otherwise 1
+\begin{itemize}
+	\item if F = $u>v$  
+		\subitem $E_{pk}(result) \gets E_{pk}(alpha)$
+	\item else	
+		\subitem $E_{pk}(result) \gets (E_{pk}(alpha)*E_pk(-1))^N-1$
+	\\if F was $u>v$ alpha already has 0 if u is min 1 if v
+	\\for the other function we have to subtract 1 and to get 0 if u is minimum 1 otherwise
+	\\return $E_pk(result)$
+\end{itemize}
+
+In phase two party one uses minimum function to get min index and returns that value
+\textbf{Return Minimum}\\
+P1 computes
+\begin{itemize}
+	\item $E_{pk}(u)  = BD(E_pk(u))$
+	\item $E_{pk}(v)  = BD(E_pk(v))$
+	\item $MinIndice = Minimum(E_{pk}(u),E_{pk}(v))$
+	\item for i=1 to l
+ 		\subitem $\Gamma_i \gets E_{pk}(v_i - u_i) * E_{pk}(r_i)$ where $r_i \in Z_n$
+ 		\\compute $v_i - u_i +r_i$
+ 	\item  $\Gamma' \gets \pi_1(\Gamma)$
+ 	\item send $\Gamma'$ and $MinIndice$ to P2
+\end{itemize}
+
+P2 computes
+
+\begin{itemize}
+	\item $MinIndice \gets D_{sk}(MinIndice)$
+	\item $M_i' \gets \Gamma_i^{(MinIndice}$ for $1\le i \le l$
+	\item return $M'$
+\end{itemize}
+
+P1 computes
+
+\begin{itemize}
+\item $M \gets \pi^{-1}(M')$
+\item $\lambda _i \gets M_i * E_{pk}(MinIndice)^{N-r_i}$ for i= 1 to l
+\\remove random terms from the difference so we can return the minimum
+\item $\Gamma \gets E_{pk}(u)*\lambda$
+\\this returns u if u is minimum otherwise v
+\item $E_{pk}(min(E_{pk}(u),E_{pk}(v))) = \Gamma$
+\end{itemize}
+
+Thus party one has minimum encrypted element between u \& v as required
 \subsection*{\textbf{Description}}

### 2017-12-01 hw2/normal_min.py
Removed normal_min

@@ -1,10 +1,0 @@
-from random import sample, randrange
-
-### Person 1 ###
-possible_functionalities = ["u less v", "v less u"]
-
-# (a)
-functionality = sample(possible_functionalities)
-print("Functionality: {}".fomrat(functionality))
-
-# (b)

### 2017-12-01 hw2/secure_minimum.py
Finished Adam's protocol

@@ -9,6 +9,9 @@ N = 13
 # Bit length
 l = 3
 
+# String formating for l bits 
+bit_str = '{:0' + str(l) + 'b}'
+
 # Generate pailliar keys
 public_key, private_key = paillier.generate_paillier_keypair()
 
@@ -37,10 +40,7 @@ def secure_multiplication(a, b):
 def minimum(u, v):
 	### Party 1 ###
 	# Randomly choose functionality
-	f = choice(["u > v"])#, "u < v"])
-
-	# String formating for l bits 
-	bit_str = '{:0' + str(l) + 'b}'
+	f = choice(["u > v", "u < v"])
 
 	# Initalize H_0
 	h_i = public_key.encrypt(0)
@@ -103,20 +103,61 @@ def minimum(u, v):
 		return (e_alpha + (public_key.encrypt(-1) * N)) - 1 # Double check
 
 
-x = 7
-y = 5
+x = 3
+y = 7
 
 #c = secure_multiplication(a, b)
 #print(private_key.decrypt(c) % N)
 
 ##### Phase 2 #####
+### Party 1 ###
 a = public_key.encrypt(x)
 b = public_key.encrypt(y)
 
-min_index = minimum(a, b)
-print(private_key.decrypt(min_index))
+# Min Index
+min_index = public_key.encrypt(private_key.decrypt(minimum(a, b)) % N) # Mod Field
+print("u < v: {}".format(private_key.decrypt(min_index)))
+
+# Gamma
+gamma = []
+r = []
+for i in range(l):
+	r.append(randrange(0, N))
+	gamma.append(public_key.encrypt(int(bit_str.format(y)[i]) - int(bit_str.format(x)[i])) + \
+		public_key.encrypt(r[-1]))
+
+# Permutation
+#shuffle(gamma)
+
+### Party 2 ### (permuted gamma and min_index)
+d_min_index = private_key.decrypt(min_index)
+
+m_prime = []
+for i in range(l):
+	m_prime.append(gamma[i] * d_min_index)
+
+### Party 1 ### (m_prime)
+
+# Lambda
+lam = []
+for i in range(l):
+	lam.append(m_prime[i] + (min_index * (N - r[i])))
 
 
+# Gamma
+gamma = []
+for i in range(l):
+	gamma.append(public_key.encrypt(int(bit_str.format(x)[i])) + lam[i])
+
+# Move back in field, and then to binary
+for i in range(l):
[…]

### 2017-12-01 hw2/secure_minimum.py
Lots of prints

@@ -41,6 +41,7 @@ def minimum(u, v):
 	### Party 1 ###
 	# Randomly choose functionality
 	f = choice(["u > v", "u < v"])
+	print("f: {}".format(f))
 
 	# Initalize H_0
 	h_i = public_key.encrypt(0)
@@ -52,13 +53,18 @@ def minimum(u, v):
 	# L list
 	L = []
 
+
 	for i in range(l):
+		print("For {} in {}".format(i, l))
 		# Assume we can get each bit out of encrypted text
 		u_i = public_key.encrypt(int(bit_str.format(x)[i]))
 		v_i = public_key.encrypt(int(bit_str.format(y)[i]))
+		print("U_{} = {}".format(i, private_key.decrypt(u_i)))
+		print("V_{} = {}".format(i, private_key.decrypt(v_i)))
 
 		# Secure minimum
 		e_ui_times_vi = secure_multiplication(u_i, v_i)
+		print("Secure Multiplication: E({})".format(private_key.decrypt(e_ui_times_vi) % N))
 		#print(private_key.decrypt(e_ui_times_vi) % N)
 
 		# Assign w_i based on f
@@ -68,42 +74,61 @@ def minimum(u, v):
 		else:
 			w_i = v_i + (e_ui_times_vi * (N - 1))
 
+		print("W_{} = E({})".format(i, private_key.decrypt(w_i) % N))
+
 		# G_i
 		g_i = public_key.encrypt(int(bit_str.format(x)[i]) ^ int(bit_str.format(y)[i]))
+		print("G_{} = E(U_{} XOR V_{}) = E({})".format(i, i, i, private_key.decrypt(g_i) % N))
 
 		# H_i
 		s.append(randrange(0, N))
 		h_i = (h_i * s[-1]) + g_i
+		print("H_{} = E({})".format(i, private_key.decrypt(h_i) % N))
 
 		# Phi
 		phi_i = public_key.encrypt(-1) + h_i
+		print("Φ_{} = E({})".format(i, private_key.decrypt(phi_i) % N))
 
 		# L_i
 		t.append(randrange(0, N))
 		l_i = w_i + (phi_i * t[-1])
+		print("L_{} = W_{} * Φ^t_{} = E({}) * E({})^{} = E({})".format(\
+			i, i, i, private_key.decrypt(w_i) % N, private_key.decrypt(phi_i) % N, \
+			t[-1], private_key.decrypt(l_i) % N))
 		L.append(l_i)
 
+	print("E(L): ", end='')
[…]

### 2017-12-03 hw2/h2.tex
fixed type changed to ^(n-1) not ^N -1
Finished example

@@
 \usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
+\usepackage{hyperref}
 % These packages are all incorporated in the memoir class to one degree or another...
@@
 	\item else	
-		\subitem $E_{pk}(result) \gets (E_{pk}(alpha)*E_pk(-1))^N-1$
+		\subitem $E_{pk}(result) \gets (E_{pk}(alpha)*E_pk(-1))^{N-1}$
 	\\if F was $u>v$ alpha already has 0 if u is min 1 if v
@@
 \subsection*{\textbf{Example}}
+The above algorithm is implemented at: \url{https://github.com/drc14/Secure_Minimum}. The example was generated using the program implemented.
+
+\textbf{Minimum(E(u), E(v))} \\
+\textbf{Party 1} \\
+Choose random functionality f: u $>$ v \\
+For 1 in 3: \\
+\indent $E(u_1) = E(1)$ \\
+\indent $E(v_1) = E(1)$ \\
+\indent $E(u_1 * v_1) =  Secure_Multiplication(E(u_1), E(v_1)) = E(1)$ \\
+\indent F: u $>$ v: \\
+\indent \indent $W_1 = E(0)$ \\
+\indent $G_1 = E(u_1 \oplus v_1) = E(0)$ \\
+\indent $H_1 = E(0)$ \\
+\indent $\Phi_1 = E(12)$ \\
+\indent $L_1 = W_1 * \Phi^(t_1) = E(0) * E(12)^8 = E(5)$ \\
+For 2 in 3: \\
+\indent $E(u_2) = E(1)$ \\
+\indent $E(v_2) = E(0)$ \\
+\indent $E(u_2 * v_2) = Secure_Multiplication(E(u_2), E(v_2)) = E(0)$ \\
+\indent F: u $>$ v: \\
+\indent \indent $W_2 = E(1)$ \\
+\indent $G_2 = E(u_2 \oplus v_2) = E(1)$ \\
+\indent $H_2 = E(1)$ \\
+\indent $\Phi_2 = E(0)$ \\
+\indent $L_2 = W_2 * \Phi^(t_2) = E(1) * E(0)^{10} = E(1)$ \\
+For 3 in 3: \\
+\indent $E(u_3) = E(1)$ \\
+\indent $E(v_3) = E(1)$ \\
+\indent $E(u_3 * v_3) = Secure_Multiplication(E(u_3), E(v_3)) = E(1)$ \\
+\indent F: u $>$ v: \\
+\indent \indent $W_3 = E(0)$ \\
+\indent $G_3 = E(u_3 \oplus v_3) = E(0)$ \\
+\indent $H_3 = E(2)$ \\
+\indent $\Phi_3 = E(1)$ \\
+\indent $L_3 = W_3 * \Phi^(t_3) = E(0) * E(1)^{2} = E(2)$ \\
+$E(L) = E(5, 1, 2)$ \\
+$E(L') = E(2, 1, 5)$ \\ \\
+
+\textbf{Party 2} \\
+$M = D(E(L')) = [2, 1, 5]$ \\
+$\alpha = 1$ because 1 appears in $M$\\
+$E(\alpha) = E(1)$ \\ \\
+\textbf{Party 1} \\
+$F: u > v$ \\
+\indent Return $E(\alpha) = E(1)$ \\ \\
+
+\textbf{Party 1} \\
+E(u) = BD(E(7)) \\ 
+E(v) = BD(E(5)) \\
+Minimum\_Index $= Mininimum(E(u), E(v)) = E(1)$ \\
+For $i=1$ to 3:
+\indent $Gamma_1 = E(v_1 - u_1) * E(r_1) = E(1 - 1) * E(5) = E(5)$ \\
+\indent $Gamma_2 = E(v_2 - u_2) * E(r_2) = E(0 - 1) * E(10) = E(9)$ \\
+\indent $Gamma_3 = E(v_3 - u_3) * E(r_3) = E(1 - 1) * E(8) = E(8)$ \\
+$\Gamma = E(5, 9, 8)$ \\
+$\Gamma' = \pi_1(\Gamma) = E(9, 8, 5)$ \\ \\
+
+\textbf{Party 2} \\
+\textit{$Min_Index = D(E(Min_Index)) = 1$} \\ 
+$M' = E(9, 8, 5)^1 = E(9, 8, 5)$ \\ \\
+
+\textbf{Party 1} \\
+$M = \pi^{-1}(M') = E(5, 9, 8)$ \\
+$\lambda = M * E(\textit{Min\_Index})^{N - r_i} = E(4, 11, 10)$ \\
+$\Gamma = E(u) * \lambda = E(5)$ \\
+$E(min(E(u), E(v))) = \Gamma = E(5)$ \\
 

### 2017-12-03 hw2/test.py

@@ -40,8 +40,7 @@ def secure_multiplication(a, b):
 def minimum(u, v):
 	### Party 1 ###
 	# Randomly choose functionality
-	f = choice(["u > v"])#, "u < v"])
-	print("f: {}".format(f))
+	f = choice(["u > v", "u < v"])
 
 	# Initalize H_0
 	h_i = public_key.encrypt(0)
@@ -53,18 +52,13 @@ def minimum(u, v):
 	# L list
 	L = []
 
-
 	for i in range(l):
-		print("For {} in {}".format(i, l))
 		# Assume we can get each bit out of encrypted text
 		u_i = public_key.encrypt(int(bit_str.format(x)[i]))
 		v_i = public_key.encrypt(int(bit_str.format(y)[i]))
-		print("U_{} = {}".format(i, private_key.decrypt(u_i)))
-		print("V_{} = {}".format(i, private_key.decrypt(v_i)))
 
 		# Secure minimum
 		e_ui_times_vi = secure_multiplication(u_i, v_i)
-		print("Secure Multiplication: E({})".format(private_key.decrypt(e_ui_times_vi) % N))
 		#print(private_key.decrypt(e_ui_times_vi) % N)
 
 		# Assign w_i based on f
@@ -74,54 +68,35 @@ def minimum(u, v):
 		else:
 			w_i = v_i + (e_ui_times_vi * (N - 1))
 
-		print("W_{} = E({})".format(i, private_key.decrypt(w_i) % N))
-
 		# G_i
 		g_i = public_key.encrypt(int(bit_str.format(x)[i]) ^ int(bit_str.format(y)[i]))
-		print("G_{} = E(U_{} XOR V_{}) = E({})".format(i, i, i, private_key.decrypt(g_i) % N))
 
 		# H_i
 		s.append(randrange(0, N))
 		h_i = (h_i * s[-1]) + g_i
-		print("H_{} = E({})".format(i, private_key.decrypt(h_i) % N))
 
 		# Phi
 		phi_i = public_key.encrypt(-1) + h_i
-		print("Φ_{} = E({})".format(i, private_key.decrypt(phi_i) % N))
 
 		# L_i
 		t.append(randrange(0, N))
 		l_i = w_i + (phi_i * t[-1])
-		print("L_{} = W_{} * Φ^t_{} = E({}) * E({})^{} = E({})".format(\
[…]

### 2017-12-03 hw2/secure_minimum.py
Removed prints in secure_minimum

@@ -40,8 +40,7 @@ def secure_multiplication(a, b):
 def minimum(u, v):
 	### Party 1 ###
 	# Randomly choose functionality
-	f = choice(["u > v"])#, "u < v"])
-	print("f: {}".format(f))
+	f = choice(["u > v", "u < v"])
 
 	# Initalize H_0
 	h_i = public_key.encrypt(0)
@@ -53,18 +52,13 @@ def minimum(u, v):
 	# L list
 	L = []
 
-
 	for i in range(l):
-		print("For {} in {}".format(i, l))
 		# Assume we can get each bit out of encrypted text
 		u_i = public_key.encrypt(int(bit_str.format(x)[i]))
 		v_i = public_key.encrypt(int(bit_str.format(y)[i]))
-		print("U_{} = {}".format(i, private_key.decrypt(u_i)))
-		print("V_{} = {}".format(i, private_key.decrypt(v_i)))
 
 		# Secure minimum
 		e_ui_times_vi = secure_multiplication(u_i, v_i)
-		print("Secure Multiplication: E({})".format(private_key.decrypt(e_ui_times_vi) % N))
 		#print(private_key.decrypt(e_ui_times_vi) % N)
 
 		# Assign w_i based on f
@@ -74,54 +68,35 @@ def minimum(u, v):
 		else:
 			w_i = v_i + (e_ui_times_vi * (N - 1))
 
-		print("W_{} = E({})".format(i, private_key.decrypt(w_i) % N))
-
 		# G_i
 		g_i = public_key.encrypt(int(bit_str.format(x)[i]) ^ int(bit_str.format(y)[i]))
-		print("G_{} = E(U_{} XOR V_{}) = E({})".format(i, i, i, private_key.decrypt(g_i) % N))
 
 		# H_i
 		s.append(randrange(0, N))
 		h_i = (h_i * s[-1]) + g_i
-		print("H_{} = E({})".format(i, private_key.decrypt(h_i) % N))
 
 		# Phi
 		phi_i = public_key.encrypt(-1) + h_i
-		print("Φ_{} = E({})".format(i, private_key.decrypt(phi_i) % N))
 
 		# L_i
 		t.append(randrange(0, N))
 		l_i = w_i + (phi_i * t[-1])
-		print("L_{} = W_{} * Φ^t_{} = E({}) * E({})^{} = E({})".format(\
[…]

### 2017-12-04 hw2/main.tex
Add files via upload

--- 2017-12-03 hw2/h2.tex
@@
 \subsection*{\textbf{Description}}
+Pre-work
+Set a bit length for u and v.\\
+Phase 1:\\
+	Goal:
+    To compute whether u or v is the minimum\\
+
+	Part 1:
+	First,Party 1 chooses a function. Either greater than or less than.
+	Next, for each bit, we compute a list of masks L.
+	Next, we permute these masks to create L'.
+    Party 1 sends L' to Party 2.\\
+
+	Part 2:
+	Party 2 decrypts L' to create M.
+    If any of the elements in M equals 1, $\alpha$, else it equals 0. If 1 is present, we know the function chosen in the 		beginning is true.
+    Party 2 then sends an encrypted copy of $\alpha$ \\
+
+	Part 3:
+	If alpha is 1, function is true. If alpha is 0, it is false. Map that to 0 if u is min, otherwise, map to 1.
+    If F was u > v alpha already has 0 if u is min 1 if v
+for the other function we have to subtract 1 and to get 0 if u is minimum 1, otherwise, return Epk(result)\\
+
+Phase 2:\\
+	Goal:
+    To return the calculated minimum to the requesting party.\\
+
+    First, Party 1 computes Epk(u), Epk(v), and MinIndice.
+    Next, for each bit, Party 1 computes $\Gamma$ and $\Gamma'$.
+    Lastly, Party 1 sends $\Gamma'$ and MinIndice to Party 2.\\
+
+	Party 2 then decrypts the received MinIndice.
+    With that and $\Gamma$, they compute $M_i'$.
+    Party 2 then sends M' to Party 1.\\
+
+    Party 1 then computes M from M'.
+    With that, Party 1 is able to compute $\lambda$ and $\Gamma$.
+    For each $\lambda$, Party 2 removes random terms from the differences so that the minimum can be found.
+    If $\Gamma$ is returned when computing it, u is the minimum. otherwise, v is the minimum.\\
 
